---
title: "Application of the Titius–Bode Rule to extra-solar planetary Systems"
author: "Federico Tejeiro"
date: "2 de agosto de 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Application of the Titius–Bode Rule to extra-solar planetary Systems

Los datos utilizados han sido extraídos de la **NASA Exoplanets Archive** .

La consulta realizada puedes extrasrla en este  [enlace]<https://exoplanetarchive.ipac.caltech.edu/cgi-bin/nstedAPI/nph-nstedAPI?table=exoplanets&select=pl_hostname,st_mass,st_rad,pl_pnum,pl_name,pl_orbper,pl_orbsmax,pl_orbeccen,pl_ratdor> .

Grabo las funciones...

```{r include= FALSE}

source("LeerDatos.R", local = TRUE)
source("Grafico.R", local = TRUE)

```


ontent as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r include= FALSE}
Datos <- LeerDatos("https://exoplanetarchive.ipac.caltech.edu/cgi-bin/nstedAPI/nph-nstedAPI?table=exoplanets&select=pl_hostname,st_mass,st_rad,pl_pnum,pl_name,pl_orbper,pl_orbsmax,pl_orbeccen,pl_ratdor&format=csv")
```


En total hemos analizado `r length(Datos[[1]]) `  sistemas con planetas, ya que también hemos incluido el Sol.


Ahora vamos a probar incluyendo algún gráfico


## Including Plots

Por ejemplo el Sistema Solar:

```{r pressure, echo=FALSE}

Grafico(Datos[length(Datos[[1]]),][[1]],as.numeric(unlist(Datos[length(Datos[[1]]),][[2]])))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
